Add Data

### 2025-01-27 data.qmd
Add full license texts
Clarify usage of renv

```{r, filename="create_data_dictionary.R"}
dat_source <- citation("palmerpenguins", auto = TRUE) |>
  format(bibtex = FALSE, style = "text")
```

@@

As before, if the license required adding the full license text, you would also need to copy it to `LICENSE.txt` (if not already in there).

>>>>

```{r}
dat_source <- citation("palmerpenguins", auto = TRUE) |>
  format(bibtex = FALSE, style = "text")
```

@@

As before, if the license required adding the full license text, you would also need to copy it to the project folder (if not already in there).
